DraftOne

### 2016-06-20 DraftOne.Rmd
Cleaning up document

```{r}
# Measure percent bias
beta_bias <- function(df, true_rr){
        percent_bias <- 100 * (true_rr - mean(exp(df$est))) / true_rr
        out <- data.frame(percent_bias)
        return(out)
}
beta_bias(rep_df, true_rr = 1.02)
```

@@

```{r}
# Measure coverage
coverage_beta <- function(df, true_rr){
        true_beta <- log(true_rr)
        coverage <- df$lower_ci <= true_beta & df$upper_ci >= true_beta
        out <- data.frame(coverage = sum(coverage) / nrow(df))
        return(out)
}

coverage_beta(rep_df, true_rr = 1.02)
```

>>>>

```{r}
# Measure percent bias
beta_bias 
beta_bias(rep_df, true_rr = 1.02)
```

@@

```{r}
# Measure coverage
coverage_beta 
coverage_beta(rep_df, true_rr = 1.02)
```
